### 2013-01-19 draft.tex
save

\newpage
\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}
1-2 pages
adssdadas

>>>>

\newpage
\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}
In our generation scientific and engineering community attempts to build human-like machines.
Like a man, these robots are supposed to have various senses, ability to analyse incoming information, based on its conclusions and develop and implement behaviour patterns.
And starting to implement, scientists immediately came across a problem of image understanding.
There are a lot of engineering achievements that supersede analogues of the most perfect system - human.
However, there is a large gap between human and machine in the technology of artificial intelligence.
Impossibility to fully automate analysis of information from visual channel, even as a child level, pushes researchers to move forward gradually.
They divide the problem into sub-problems of computer vision. 
For example, improving image quality, identifying features points and determining the similarity of images.

The vision channel is one of the most informative ones.
Data volume from video stream exceeds by several times volumes from other sensors.
Here lies the pitfall - redundancy of information.
%Иногда бывает достаточно нескольких байт информации
Occasionally just a few bytes of information are enough.
For example, we need only the object of interest, and in addition to this, we have other objects, background and fine detail.
In contrast to human, the machine can not optimally handle this task.
Consequence of this problem is the fact that even an ant can navigate better in the complicated situation than existing robots.

Why is the task of understanding the image so complex?
In the image processing we can come across several problems.
Firstly, objects of observations are very volatile in general.
Causes of variability are difficult to formalize.
Existing methods of dealing with different lighting, noises and distortions cope rather clumsily.
Secondly, scene observations also can not be modelled.
This is due to the fact that there is a diversity of geometrical forms, colors and textures.
Third problem is knowledge base.
Any system required to recognize an object should be aware of it.
It means that system should be trained to recognize images.
People, during their life, spend a lot of time doing it.
